### 2019-03-18 README.Rmd
Add pkgdown

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
knitr::opts_chunk$set(cache = TRUE)
```

@@

>>>>

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
knitr::opts_chunk$set(cache = TRUE)
citesdb::cites_disconnect()
MonetDBLite::monetdblite_shutdown()
```

@@

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
cites_disconnect()
```
